\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% --- METADATA ADDITION ---
\hypersetup{
    pdftitle={Yeshwanth Krishna - SDE Resume},
    pdfauthor={Yeshwanth Krishna},
    pdfsubject={Software Development Engineer},
    pdfkeywords={MERN, Next.js, Distributed Systems, NSRY, AI, SDE}
}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Yeshwanth Krishna} \\ \vspace{1pt}
    \href{tel:917063929660}{\small +91 7063929660} $|$ \href{mailto:yeshwanthkrishna37@gmail.com}{\small{yeshwanthkrishna37@gmail.com}} $|$ 
    \href{https://linkedin.com/in/yeshwanth-kr}{\small{LinkedIn}} $|$
    \href{https://github.com/Yeshwanth-kr}{\small{Github}} $|$
    \href{https://yeshwanth.online}{\small{Portfolio}}
\end{center}

%-----------SUMMARY-----------
\section{Professional Summary}
 \small{
  Software Development Engineer at \textbf{NSRY, SVP} with a proven track record of architecting scalable MERN stack applications and integrating AI-driven analytics. Experienced in optimizing mission-critical systems, reducing production errors by 30\%, and delivering high-concurrency real-time platforms. Committed to operational excellence and technical ownership in fast-paced, high-stakes environments.
 }

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript (ES6+), TypeScript, C++, Python, SQL, HTML/CSS} \\
     \textbf{Frameworks}{: React.js, Next.js 15, Node.js, Express.js, Redux Toolkit} \\
     \textbf{Tools}{: Git, Docker, AWS (EC2, S3), Jest, Cypress, Redis} \\
     \textbf{Leadership}{: Ownership, Customer Obsession, Bias for Action, Deliver Results, Operational Excellence}
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Development Engineer}{Sep 2025 -- Present}
      {NSRY, SVP (Naval Ship Repair Yard)}{Sri Vijaya Puram, India}
      \resumeItemListStart
        \resumeItem{Architected and refactored core MERN modules for industrial resource management, improving backend responsiveness and data retrieval speed.}
        \resumeItem{Reduced production-level system errors by 30\% by implementing a comprehensive automated testing suite using Jest and Cypress for mission-critical logic.}
        \resumeItem{Digitized legacy industrial workflows into scalable full-stack applications, ensuring high data integrity and operational reliability in a high-stakes environment.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Full-Stack Engineering Consultant}{Jan 2024 -- Present}
      {Independent / Freelance}{Remote}
      \resumeItemListStart
        \resumeItem{Managed full-cycle SDLC for diverse clients, delivering production-ready platforms using Next.js 15, TypeScript, and AWS.}
        \resumeItem{Optimized database schemas and API orchestration layers, resulting in a 40\% average increase in client Lighthouse performance scores.}
        \resumeItem{Integrated third-party services including secure payment gateways and LLM-based automation (Gemini 2.0) into existing enterprise systems.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AI-ATS Analytics Engine} $|$ \emph{React, Node.js, Gemini 2.0, MongoDB}}{$(${\href{https://ats.yeshwanth.online}{Live App}} $|$ {\href{https:github.com/yeshwanth-kr/ai-ats-engine}{Code}}$)$}
          \resumeItemListStart
            \resumeItem{Built an intelligence platform utilizing Gemini 2.0 for resume-JD alignment, featuring automated parsing and real-time recruitment scoring.}
            \resumeItem{Developed prompt-chaining logic to deliver deep behavioral insights and technical gap analysis for high-volume hiring pipelines.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Real-time Collaboration Platform} $|$ \emph{Next.js, Socket.io, Redis, JWT}}{$(${\href{https://wishlist.yeshwanth.online}{Live App}} $|$ {\href{https://github.com/Yeshwanth-kr/realtime-collab-platform}{Code}}$)$}
          \resumeItemListStart
            \resumeItem{Engineered a distributed synchronization engine achieving sub-100ms latency for concurrent real-time state management.}
            \resumeItem{Implemented room-based isolation and persistent ledger systems to ensure data consistency across multiple client nodes.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Pathfinding Analysis Engine} $|$ \emph{JavaScript, Canvas API, DSA}}{$(${\href{https://visualize.yeshwanth.online}{Live App}} $|$ {\href{https://github.com/Yeshwanth-kr/pathfinding-visualizer-pwa}{Code}}$)$}
          \resumeItemListStart
            \resumeItem{Architected a PWA to benchmark search heuristics (A*, Dijkstra) on complex grids, optimizing for 60FPS rendering of 2500+ nodes.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {KL University}{Vijayawada, India}
      {Bachelor of Computer Applications}{CGPA: 8.95}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}