\documentclass[letterpaper,11pt]{article}

\usepackage{microtype}
\usepackage{ragged2e}
\justifying
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% --- METADATA ADDITION ---
\hypersetup{
    pdftitle={Yeshwanth Krishna - SDE Resume},
    pdfauthor={Yeshwanth Krishna},
    pdfsubject={Software Development Engineer},
    pdfkeywords={MERN, Next.js, Distributed Systems, NSRY, AI, SDE}
}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Yeshwanth Krishna} \\ \vspace{1pt}
    \href{tel:917063929660}{\small +91 7063929660} $|$ \href{mailto:yeshwanthkrishna37@gmail.com}{\small{yeshwanthkrishna37@gmail.com}} $|$ 
    \href{https://linkedin.com/in/yeshwanth-kr}{\small{LinkedIn}} $|$
    \href{https://github.com/Yeshwanth-kr}{\small{Github}} $|$
    \href{https://yeshwanth.online}{\small{Portfolio}}
\end{center}

%-----------SUMMARY-----------
\section{Professional Summary}
 \small{
  Software Engineer with hands-on experience building scalable MERN stack applications and AI-augmented development workflows. Proven ability to improve system reliability (30\% reduction in production errors) and leverage AI tooling to accelerate delivery and optimize real-time, high-concurrency systems. Strong ownership mindset with a focus on performance, correctness, and maintainability.
 }

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript (ES6+), TypeScript, C++, Python, SQL, HTML/CSS} \\
     \textbf{Frameworks}{: React.js, Next.js 15, Node.js, Express.js, Redux Toolkit} \\
     \textbf{Tools}{: Git, Docker, AWS (EC2, S3), Jest, Cypress, Redis} \\
     \textbf{Core CS}{: Data Structures, Algorithms, OOP, REST APIs, System Design} \\
     \textbf{Leadership}{: Code Review, Agile/Scrum, Cross-functional Collaboration, Technical Documentation, Mentoring}
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Development Engineer}{Sep 2025 -- Present}
      {NSRY, SVP (Naval Ship Repair Yard)}{Sri Vijaya Puram, India}
      \resumeItemListStart
        \resumeItem{Architected and refactored core MERN modules for industrial resource management, improving backend responsiveness and data retrieval speed.}
        \resumeItem{Reduced production-level system errors by 30\% by implementing a comprehensive automated testing suite using Jest and Cypress for mission-critical logic.}
        \resumeItem{Digitized legacy industrial workflows into scalable full-stack applications, ensuring high data integrity and operational reliability in a high-stakes environment.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Full-Stack Engineering Consultant}{Jan 2023 -- Present}
      {Independent / Freelance}{Remote}
      \resumeItemListStart
        \resumeItem{Managed full-cycle SDLC for diverse clients, delivering production-ready platforms using Next.js 15, TypeScript, and AWS.}
        \resumeItem{Optimized database schemas and API orchestration, improving Lighthouse performance scores by ~40\% while maintaining backward compatibility for existing users.}
        \resumeItem{Integrated third-party services including secure payment gateways and LLM-based automation (Gemini 2.0) into existing enterprise systems.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{ScratchPad} $|$ \emph{React, TypeScript, Rough.js, Canvas API, Vite}}{$(${\href{https://scratchpad.yeshwanth.online}{Live App}} $|$ {\href{https://github.com/yeshwanth-kr/scratchpad}{Code}}$)$}
          \resumeItemListStart
            \resumeItem{Built a fully functional Excalidraw-inspired whiteboard application using React and Canvas API, implementing a custom geometric state model for drawing, resizing, panning, and undo/redo operations.}
            \resumeItem{Hardened the project with a production-grade DevSecOps pipeline using GitHub Actions, Docker, Lighthouse CI, and Dependabot — achieving zero high-severity vulnerabilities and enforced Core Web Vitals budgets on every deployment.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Veloce Kanban} $|$ \emph{React, TypeScript, DnD-Kit, Framer Motion, Tailwind CSS}}{$(${\href{https://veloce.yeshwanth.online}{Live App}} $|$ {\href{https://github.com/Yeshwanth-kr/veloce-kanban}{Code}}$)$}
          \resumeItemListStart
            \resumeItem{Engineered a high-performance Kanban board with fluid drag-and-drop mechanics across dynamic containers using DnD-Kit, with persistent state management and polished layout animations via Framer Motion.}
            \resumeItem{Designed with full TypeScript type safety and a minimalist Tailwind CSS aesthetic, inspired by Jira, Trello, and Notion UI patterns.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Pathfinding Analysis Engine} $|$ \emph{JavaScript, Canvas API, DSA}}{$(${\href{https://visualize.yeshwanth.online}{Live App}} $|$ {\href{https://github.com/Yeshwanth-kr/pathfinding-visualizer-pwa}{Code}}$)$}
          \resumeItemListStart
            \resumeItem{Architected a PWA to benchmark search heuristics (A*, Dijkstra) on complex grids, optimizing for 60FPS rendering of 2500+ nodes.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {KL University}{Vijayawada, India}
      {Bachelor of Computer Applications}{CGPA: 8.95}
      \resumeItem{Relevant Coursework: Data Structures, Algorithms, Operating Systems, Networking}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}