\documentclass[letterpaper,11pt]{article}

\usepackage{microtype}
\usepackage{ragged2e}
\justifying
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% --- METADATA ADDITION ---
\hypersetup{
    pdftitle={Yeshwanth_Krishna - IT Support Engineer Resume},
    pdfauthor={Yeshwanth Krishna},
    pdfsubject={IT Support Engineer / Infrastructure Engineer},
    pdfkeywords={Active Directory / DNS / DHCP, Ticketing Systems, Root Cause Analysis (RCA), SLA Management, Asset Lifecycle}
}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Yeshwanth Krishna} \\ \vspace{1pt}
    \href{tel:917063929660}{\small +91 7063929660} $|$ \href{mailto:yeshwanthkrishna37@gmail.com}{\small{yeshwanthkrishna37@gmail.com}} $|$ 
    \href{https://linkedin.com/in/yeshwanth-kr}{\small{LinkedIn}} $|$
    \href{https://github.com/Yeshwanth-kr}{\small{Github}} $|$
    \href{https://yeshwanth.online}{\small{Portfolio}}
\end{center}

%-----------SUMMARY-----------
\section{Professional Summary}
 \small{
  IT Support Professional with 2 years of experience managing corporate technical infrastructure and providing high-level support for internal customers. Proven expertise in troubleshooting LAN/WAN, managing Windows/Linux environments, and resolving complex hardware/software issues. Strong focus on Operational Excellence and reducing system downtime through proactive asset management and incident resolution.
 }

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Networking}{: Cisco, Nivetti, Tejas Switches; TCP/IP, VLAN, Routing/Switching, Fiber \& Copper Cabling} \\
     \textbf{Hardware}{: Dell PowerEdge, HPE ProLiant, Rack \& Stack, Break-Fix, RMA Processing, Cable Management (Cat6/Fiber), PDU/UPS Management, DCIM Tools} \\
     \textbf{Operating Systems}{: Windows 10/11, Windows Server (Active Directory, DHCP, DNS), macOS, Linux} \\
     \textbf{Tools}{: Shell Scripting, SCCM, CLI, Docker, Jenkins, Hardware Health Monitoring} \\
     \textbf{IT Operations}{: Ticketing Systems (Jira), Asset Management, Procurement, Disaster Recovery} \\
     \textbf{Tools \& Equipment}{: OTDR, Cable Testers, Crimping Tools, Label Makers, Rack Mounting Hardware, Serial Consoles} \\
     \textbf{Leadership}{: Incident Response, Change Management, Shift Handover Documentation, Vendor Coordination} 
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {IT Support \& Systems Engineer}{Sep 2025 -- Present}
      {NSRY, SVP (Naval Ship Repair Yard)}{Sri Vijaya Puram, India}
\resumeItemListStart
        \resumeItem{Manage high-level network engineering for the Naval Communication Network, specializing in the configuration and deployment of enterprise-grade Cisco, Nivetti, and Tejas switches.}
        \resumeItem{Perform break-fix repairs and RMA processing on Dell/HPE server hardware, maintaining 24/7 uptime for critical naval resource management systems.}
        \resumeItem{Perform structured cabling (fiber and copper), hot/cold aisle management, and rack-level power distribution (PDU/UPS) to maintain thermal efficiency and uptime.}
        \resumeItem{ Execute complex password recovery and firmware update protocols on legacy and modern networking hardware to restore system connectivity and security.}
        \resumeItem{Coordinate onsite technical maintenance and rack-level deployments, ensuring strict adherence to safety and operational reliability standards in a high-stakes environment.}
        \resumeItem{Manage user account administration and troubleshoot domain trust relationship issues via Active Directory, resolving endpoint authentication failures and account lockouts to minimize user downtime.}
      \resumeItemListEnd
      
\resumeSubheading
      {Infrastructure and Deployment Consultant}{Jan 2023 -- Present}
      {Independent / Freelance}{Remote}
      \resumeItemListStart
        \resumeItem{Performed physical server installation, rack mounting, and network configuration for a client hosting environment, ensuring stable connectivity and optimal hardware placement for production workloads.}
        \resumeItem{Deployed and maintained on-premise server infrastructure for clients, integrating hardware health monitoring tools to track system performance and data integrity across distributed nodes.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------KEY ACHIEVEMENTS-----------
\section{Key Achievements}
    \resumeItemListStart
    \resumeItem{Led a full-scale network migration across a high-security naval facility, consolidating isolated network segments into a unified infrastructure — playing a key role in endpoint migration and switch configuration.}
    \resumeItem{Diagnosed and resolved a recurring underwater OFC cable fault in a marine environment using OTDR testing, identifying and restoring connectivity to a naval floating dock each time the fault occurred.}
    \resumeItem{Recovered a wall-mounted rack collapse during live operations, re-deploying and restoring full connectivity within 15 minutes, maintaining near-zero unplanned downtime.}
    \resumeItem{Maintained 24/7 network availability across a classified naval facility throughout tenure, with only 1–2 recorded downtime incidents over the entire period.}
    \resumeItemListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {KL University}{Vijayawada, India}
      {Bachelor of Computer Applications}{CGPA: 8.95}
      \resumeItem{Relevant Coursework: Data Structures, Algorithms, Operating Systems, Networking}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
