\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% --- METADATA ADDITION ---
\hypersetup{
    pdftitle={Yeshwanth Krishna - Data Center Technician Resume},
    pdfauthor={Yeshwanth Krishna},
    pdfsubject={Data Center Technician / Infrastructure Engineer},
    pdfkeywords={Networking, Cisco, Nivetti, Hardware Troubleshooting, Server Maintenance, Rack Deployment, Linux, Operational Excellence, Amazon Leadership Principles, DCT}
}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Yeshwanth Krishna} \\ \vspace{1pt}
    \href{tel:917063929660}{\small +91 7063929660} $|$ \href{mailto:yeshwanthkrishna37@gmail.com}{\small{yeshwanthkrishna37@gmail.com}} $|$ 
    \href{https://linkedin.com/in/yeshwanth-kr}{\small{LinkedIn}} $|$
    \href{https://github.com/Yeshwanth-kr}{\small{Github}} $|$
    \href{https://yeshwanth.online}{\small{Portfolio}}
\end{center}

%-----------SUMMARY-----------
\section{Professional Summary}
 \small{
  Systems and Network Professional with hands-on experience in high-density data environments and mission-critical infrastructure. Proven expertise in configuring enterprise-grade networking equipment (Cisco, Nivetti, Tejas) and managing complex hardware lifecycle tasks. Strong ownership mindset with a focus on operational excellence, hardware reliability, and maintaining 100\% system availability in industrial and naval environments.
 }

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Networking}{: Cisco, Nivetti, Tejas Switches; TCP/IP, VLAN, Routing/Switching, Fiber \& Copper Cabling} \\
     \textbf{Hardware}{: Server Rack Maintenance, Component Replacement (CPU, RAM, NIC), PSU Diagnostics, Troubleshooting} \\
     \textbf{OS \& Tools}{: Linux (Ubuntu, Debian), Shell Scripting, CLI, Docker, Jenkins, Hardware Health Monitoring} \\
     \textbf{Leadership}{: Ownership, Customer Obsession, Bias for Action, Deliver Results, Operational Excellence} \\
     \textbf{Infrastructure}{: Power Distribution, Thermal Management, SLA Adherence, Asset Tracking, Security Protocols}
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Systems and Network Engineer}{Sep 2025 -- Present}
      {NSRY, SVP (Naval Ship Repair Yard)}{Sri Vijaya Puram, India}
\resumeItemListStart
        \resumeItem{Manage high-level network engineering for the Naval Communication Network, specializing in the configuration and deployment of enterprise-grade Cisco, Nivetti, and Tejas switches.}
        \resumeItem{Perform hardware-level diagnostics and component-level repairs on server-side infrastructure, maintaining 24/7 uptime for critical naval resource management systems.}
        \resumeItem{Execute complex password recovery and firmware update protocols on legacy and modern networking hardware to restore system connectivity and security.}
        \resumeItem{Coordinate onsite technical maintenance and rack-level deployments, ensuring strict adherence to safety and operational reliability standards in a high-stakes environment.}
      \resumeItemListEnd
      
\resumeSubheading
      {Infrastructure and Deployment Consultant}{Jan 2023 -- Present}
      {Independent / Freelance}{Remote}
      \resumeItemListStart
        \resumeItem{Managed full-cycle deployment and infrastructure scaling for diverse clients, utilizing Docker and Jenkins to automate CI/CD pipelines and reduce manual intervention.}
        \resumeItem{Optimized server-side resource allocation and database orchestration, improving system responsiveness by 40\% and ensuring high availability for enterprise applications.}
        \resumeItem{Integrated secure monitoring tools to track hardware health and data integrity across distributed cloud and on-premise nodes.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Distributed Infrastructure Monitor} $|$ \emph{Docker, Jenkins, MongoDB, Shell}}{}
          \resumeItemListStart
            \resumeItem{Developed a monitoring engine to benchmark hardware performance and connectivity across distributed nodes, utilizing Jenkins for automated health checks.}
            \resumeItem{Implemented real-time alert systems for hardware failures and network latency spikes, ensuring rapid incident response and resolution.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Marine Access Management System} $|$ \emph{Node.js, SQL, Security Protocols}}{}
          \resumeItemListStart
            \resumeItem{Architected a secure vendor management system for a marine dockyard, focusing on high data integrity and secure physical access control protocols.}
            \resumeItem{Managed the deployment and server-side configuration to handle high-concurrency requests while maintaining sub-100ms processing speeds.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {KL University}{Vijayawada, India}
      {Bachelor of Computer Applications}{CGPA: 8.95}
      \resumeItem{Relevant Coursework: Data Structures, Algorithms, Operating Systems, Networking}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
